% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xspace}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{amsmath}

\def\name{Gerard Vico}

% PDF metadata
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {scala, java, software development, algorithms, computer science, functional programming},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\newenvironment{no-indent-itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\def\tilde{$\scriptstyle\sim$}
\def\bullet{$\circ$\xspace}

\begin{document}

{\huge \name}

\bigskip
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{llll}
    Mobile: & On request %+44 7722 958465
    Email: & \href{mailto:gerard.vico@gmail.com}{\tt gerard.vico@gmail.com} 
       & GitHub: &\href{https://github.com/HDBandit}{\tt https://github.com/HDBandit}\\
    Languages: & \textsc{sp}, \textsc{en}, \textsc{cat}       
  \end{tabular}
\end{minipage}

\bigskip
\textsc{Keywords}: 
AWS, EC2, DynamoDB, MySQL, SQS, SNS, JSON, REST, SOLID, Microservices, Scala, Java, Play 2.x, SBT, Java, Spring, Spring Boot, Spring Cloud, Maven,
Akka, Akka Cluster, Actor Model, Docker, JUnit, Mockito, Git, Jira, Agile, Scrum.

\section*{Employment}
\begin{no-indent-itemize}
%  \item \textsc{Google}, Software Engineer, Oct 2018--present.
%  \begin{itemize}
%  \end{itemize}
  \item \textsc{Letgo}, Scala Software Engineer, June 2016--Present.
  \begin{itemize}
    \item\bullet Developed a distributed chat application based on web sockets with Play framework, Scala, Akka Actors Model and Akka Cluster.
    \item\bullet Solve platform scalability problems (sharding WS connections).
    \item\bullet Refactored legacy code following best practices.
    \item\bullet On-call and hot fix responsibility for such services.
  \end{itemize}
  \item \textsc{Zyncro}, Java Software Engineer, Dec 2015--Apr 2016.
  \begin{itemize}
    \item\bullet Developed first high-load mobile API micro-service in Scala, 1000+ rps.
    \item\bullet Implemented a crawler to monitor the content and the availability of home and campaign pages.
    \item\bullet Built a caching layer with Clojure and ElasticCache to tell the login status of a customer.
    \item\bullet Set architectural patterns in the Android app to improve test coverage.
    \item\bullet Decreased Android app startup time by \tilde 65\% and crash rate to <0.5\%.
    \item\bullet Built a Chrome extension to inject OAuth 2.0 tokens into URL ranges to improve dev productivity.
    \item\bullet Interviewed countless developers, juniors to leads, doubling the Android team in less than 6 months.
    \item\bullet Given internal workshops on testability, unit testing, and code quality.
    \item\bullet Mentored new developers, especially in functional languages like Scala.
  \end{itemize}
  \item \textsc{Grifols}, Java Software Engineer, Jan 2007--Dec 2015.
  \begin{itemize}
    \item\bullet Prototyped and responsible for architecture of Cortado Corporate and Templace.
    \item\bullet Implemented key components such as preview, navigation, file operations, favorites, and others.
    \item\bullet Ported and adapted Personal Printing, a print job managing app.
    \item\bullet Collaborated with UX and product teams to assess requirements.
  \end{itemize}
  \item \textsc{Indra}, Java Software Engineer, Feb 2006--Dec 2006. 
  \begin{itemize}
    \item\bullet Developed a web services layer for Banc Sabadell.
    \item\bullet Developed a frontend based on Zk framework (Ajax).
  \end{itemize}
\end{no-indent-itemize}

\section*{Education}
\begin{no-indent-itemize}
  \item UNIVERSIDAD POLITÉCNICA DE CATALUÑA, Barcelona (Computer Systems Engineer) 2002--2006
\end{no-indent-itemize}

\section*{Continuous Learning and Certifications}
\begin{no-indent-itemize}
  \item Oracle Certified Programmer, Java SE 7 (OCPJP, formerly SCJP)
\end{no-indent-itemize}


\bigskip
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
